%!TEX root=../icsme2016-mrstudyr.tex

\vspace*{-.25em}

% \section{\textit{mrstudyr}: Mutant Reduction Studier}
\section{Implementation and Use of the \mr~Tool}

\subsection{Objectives}

% CJM: Moving this figure to usage section to allow the reader to visualise the process
% \input{figures/mrstudyr}

% Performing mutation testing, displayed in Figure~\ref{fig:process}, is often considered to be too expensive to take

% Review the process of mutation testing, starting with the first part at the top of the diagram

When performed with tools such as Major~\cite{Just2011b}, the process of mutation testing, as displayed in
Figure~\ref{fig:process}, involves the use of operators to generate mutants for a specific program and then the
execution of tests to determine how they kill the mutants. The outcome of this phase is the higher-is-better mutation
score, or the ratio of the number of killed mutants to the number of mutants generated~\cite{Just2011a}. In many cases,
as shown in Figure~\ref{fig:process}, it is necessary to perform various analyses of the mutants. For instance, testers
may want to see which mutants were not killed so as to determine if they are equivalent (i.e., semantically the same as
the original program) or, alternatively, indications of ways to improve the test suite.

% Start to discuss the idea of retrospective mutant analysis for reduction techniques (questions you can answer)

This paper presents another type of mutant analysis: the retrospective study of mutant reduction techniques. Leveraging
data collected during mutation testing (e.g., the name of an operator that produced a mutant, the kill-status of a
mutant, and the costs of producing and analysing a mutant), this method supports the study of mutant reduction
techniques. This type of retrospective analysis allows testers to ask and answer questions like ``what would the
mutation score be if only a random 20\% of the mutants were executed?'' While questions of this nature could be executed
through, for instance, either a manual analysis or a bespoke program, this paper presents \mr, a tool that makes it easy
to effectively pose and answer questions about methods for mutant reduction.

% GMK NOTE: This content has been cut because it was too redundant

% The first of its kind, \mr~is a tool for performing the retrospective analysis of mutant reduction techniques. Upon
% collecting generalised data from performing mutation testing on all mutants, \mr~is capable of determining efficiency
% and effectiveness of well-known mutant reduction techniques specific to the data.

% In this paper, we display that \mr~is versatile by conducting a preliminary study of mutant reduction techniques on
% mutant data collected from testing database schemas.  However, the \mr~tool is not limited to analysing mutant data from
% programs or databases, it can effectively be used in any number domains. Where mutation testing can be performed, \mr~is
% capable of analysing reduction techniques.

% The \mr~tool is not limited to the domains where it can be utilised, nor is it restricted by the reduction approaches it
% can perform.

% Talk about the reduction methods that are implemented in the tool and then explain how easy it is to add new ones
% Say that the tool is extensively documented and easy for someone to start using right away

% The tool's documentation explains the inputs, outputs, and behavior of the main functions.

Currently, \mr~can perform a widely-studied mutant reduction technique: mutant sampling~\cite{gopinath2015mutation,
jia2011analysis, gopinath2015empirical}. Due to its extensible design, the \mr~tool could be extended to perform
specific reduction techniques such as E-selective~\cite{offutt1996experimental}, where mutants are only created by the
following operators: ABS, UOI, LCR, AOR, and ROR~\cite{gopinath2015empirical}. Additionally, reduction methods that group
mutants with clustering algorithms~\cite{jia2011analysis} could also be incorporated into \mr. To support the
integration of new algorithms for mutant reduction, \mr~is accompanied with extensive documentation that explains the
inputs, outputs, and behavior of the main functions~\cite{tool}.

% GMK NOTE: This content is interesting, but not absolutely needed and not in the spirit of a research paper

% The documentation includes the necessary commands to get the reader ``up-and-running'' with \mr~quickly and obviates the
% need to read a poorly-formatted command-line manual page.

\subsection{Input Format}

% Talk about the input format of the presented tool, stressing that it is general and useful for many domains

By accepting a generalised input format, the \mr~tool can be used in a variety of testing domains to assess the
efficiency and effectiveness of mutant reduction techniques. Table~\ref{tbl:study-data} gives a snippet of a data set
analyzed in the experimental study of this paper. Organized so that each row furnishes data about an individual mutant,
\mr's data is in a ``tidy'' format~\cite{Wickham2014} that primarily focuses on the entity under test, the configuration
in which mutation testing was performed, and the operator that produced each mutant. Since mutation testing systems can
produce different types of mutants (e.g., normal, still-born, or equivalent)~\cite{Wright2014}, \mr's input files also
record the type of the mutant. Additionally, the tool tracks the status of the mutant and one of many different
execution timings (e.g., mutant generation or analysis time); as necessary, the tool can also be extended to process
more input types.

% GMK NOTE: While this content is interesting and potentially important, I don't think that we have enough space for it!

% The \mr~tool has been released on the popular Git repository hosting service, GitHub~\cite{github}
% under version 3 of the GNU General Public License~\cite{license}. The GNU General Public License
% allows for commercial, patent and private use, as well as distribution of and modification to the tool
% under the condition that anything derived from it is bound by the same conditions as the originally
% released version~\cite{copyleft}.

\input{tables/sample_data}

% GMK NOTE: All of this content has been moved to other locations of the paper

% \input{sections/mrstudyr_retrospective}
% \input{sections/mrstudyr_io}
% \input{sections/mrstudyr_calculations}
