---
title: "MRSTUDYR: Retrospectively Studying the Effectiveness of Mutant Reduction Techniques"
output:
  pdf_document:
    keep_tex: true
    highlight: pygments
    number_sections: true
---

# Installing the Ineffective Mutant Analysis Package

This code will install the ineffectivemutants package from GitHub using the `install_github` function.

```{r, echo=TRUE, message=FALSE, results='hide'}
options(scipen=10, width=200)
devtools::install_github("mccurdyc/mrstudyr")
```

> # Comparing the Mutation Scores

## Initialize the System

First, load in the libraries that are used in addition to those with the mrstudyr package (i.e., load all
of the packages not used by mrstudyr but still used in this RMarkdown file). Note that right now the
mrstudyr package will automatically load all of the packages that it needs to performs its various
analyses. Now, we are ready to call the functions from the ineffectivemutants package and produce the appropriate
summary tables and graphs.

```{r, echo=TRUE}
suppressPackageStartupMessages(library(mrstudyr))
suppressPackageStartupMessages(library(knitr))
```

## Show the Schemas for the ICSME 2016 Paper

```{r, echo=TRUE, message=FALSE, results='hide'}
sqlite_data <- read_sqlite_avmdefaults()
schemas <- sqlite_data %>% collect_study_schemas() %>%
           collect_normal_data() %>% select(schema) %>% unique()
```

## Perform Reduction Techniques

First, performing the most common reduction technique, random sampling.

```{r, echo=TRUE, message=FALSE, results='hide'}
d <- read_sqlite_avmdefaults()
normal_data <- d %>% collect_study_schemas() %>% collect_normal_data()
random_sampling_data <- normal_data %>% analyze_random_sampling()
```

Next, applying the concepts of random sampling but, over operators.

```{r, echo=TRUE, message=FALSE, results='hide'}
d <- read_sqlite_avmdefaults()
normal_data <- d %>% collect_study_schemas() %>% collect_normal_data()
operator_sampling_data <- normal_data %>% analyze_across_operators()
```
## Visualize the Mutation Scores for the Random Sampling Technique

Now, to plot the graph that shows the mutation score for the random sampling mutant
reduction technique for four user-specified percentages. In this example, we will
create a visualisation containing the percentages found in the accompanying paper.

```{r, echo=TRUE, message=FALSE, results='hide'}
d <- read_sqlite_avmdefaults()
normal_data <- d %>% collect_study_schemas() %>% collect_normal_data()
filtered_percents_data <- random_sampling_data %>% collect_chosen_percent_data(c(1, 10, 20, 40))
```

To actually create the visualization, use the following function, giving it the reduced data
from four percentages.

```{r, mutation_score_random, fig.width=5.7, fig.height=3.5, echo=TRUE}
visualize_plot_mutation_score(filtered_percents_data)
```

Analysis of the results in this graph:

- Great variability in mutation scores at percentage: 1
- Even at percentage: 10, variability in mutation scores is reduced
- The same trend remains true for percentage: 20 and 40, but a smaller reduction in variability of mutation scores

Now, plot the graph that shows the mutation score for the operator sampling mutant reduction technique.

First, select four percentages to compare.

```{r, echo=TRUE, message=FALSE, results='hide'}
d <- read_sqlite_avmdefaults()
normal_data <- d %>% collect_study_schemas() %>% collect_normal_data()
filtered_percents_data <- operator_sampling_data %>% collect_chosen_percent_data(c(1, 10, 20, 40))
```

Then, plot those four percentages against each other.

```{r, mutation_score_operator, fig.width=5.7, fig.height=3.5, echo=TRUE, message=FALSE, results='hide'}
visualize_plot_mutation_score(filtered_percents_data)
```

Analysis of the results in this graph:

- Similar to random sampling, there is great variability in mutation scores at percentage: 1
- At percentage: 10, variability in mutation scores is reduced substantially
- This trend continues for percentage: 20 and 40, but with a smaller reduction in variability of mutation scores over these percentages
